{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-12-17 documents/background.tex
just a scale issue
liposome

@@

Some Russian research has, in the past, been discounted due to attenuators that leak high

>>>>

Notice that a non-zero resonant frequency
requires
ωR 6= 0 ⇒ β < ω/√
2. (49)
That is, the oscillator must be sufficiently under-damped in order to exhibit a
resonance response

@@

Some research has been discounted due to attenuators that leak high
